---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options("max.print" = 100)
```

# finma

<!-- badges: start -->
[![R build status](https://github.com/yimi97/finma/workflows/R-CMD-check/badge.svg)](https://github.com/yimi97/finma/actions)
<!-- badges: end -->

The goal of `finma` is to provide a suite of functions to facilitate machine
learning in finance. Each function has a common prefix, `fl_`, making them
easy to identify. The functions in this package 

- compute price volatility,
- define class labels for financial time series data according to the
  triple-barrier method,
- appropriately filter financial time series data,
- partition data into training and testing with an embargo,
- implement a cross-validation procedure for financial time series data with
  options to purge and embargo data,
- and more!

## Installation

You can install the released version of `finma`
from [CRAN](https://CRAN.R-project.org) with

``` r
install.packages("finma")
```

And the development version from [GitHub](https://github.com/) with

``` r
# install.packages("devtools")
devtools::install_github("yimi97/finma")
```
## Usage

```{r example, message=FALSE}
library(finma)
library(tidyverse)
library(Quandl)
```

#### CUSUM filter

The CUSUM filter is a quality-control method, designed to detect a shift in the 
mean value of a measured quantity away from a target value. 

```{r cusum}
oil <- Quandl("NSE/OIL") %>% select(Date, Close)
oil <- zoo(oil$Close, order.by = as.Date(oil$Date))

x <- window(oil, start = "2009-09-30", end = "2012-01-01")
fl_plot_cusum(x, fl_cusum_filter(x, 100))
```

#### Triple-barrier labeling method

The triple-barrier method labels an observation according to the first barrier 
touched out of three barriers. The two horizontal barriers are defined by 
profit-taking and stop-loss limits, which are a dynamic function of an estimated 
volatility. The third barrier is defined as an expiration limit. 

```{r label}
fl_get_label(x, fl_simulate_events(x), vertial_touch_label="zero") %>% 
  select(lower, upper, t1, first_touch, return, label)
```

If the upper barrier is touched first, we label the observation as 1. If the 
lower barrier is touched first, we label the observation as -1. If the vertical 
barrier is touched first, we have two options: `sign` and `zero`. If `sign`, 
the label is decided by the sign of the asset's return. If `zero`, the label is
set to 0.

```{r echo = FALSE}
x1 <- x[1:100]
plot(x1, 
     main = "Triple-barrier labeling method", 
     xlab = "Time",
     ylab = "Price",
     col = "gray")
x0 <- as.Date("2009-12-15")
x1 <- as.Date("2010-01-15")
y0 <- 1230
y1 <- 1255
segments(x0, y0, x1, y0, col = "blue", lty = 2)
segments(x0, y1, x1, y1, col = "blue", lty = 2)
segments(x0, y0, x0, y1, col = "blue")
segments(x1, y0, x1, y1, col = "blue", lty = 2)
```

The plot is a schematic diagram of the Triple-barrier labeling method. The three 
dotted lines are two horizontal and one vertical barrier. It is shown that the 
lower barrier is touched first and this observation should be labeled -1.

#### Cross-validation

For financial time series data, which is serially correlated, the training set 
contains information that appears in the testing set. This is known as leakage. 
To prevent leakage, data scientists can use a combination of purging and 
embargo. 

```{r purged_cv}
label <- fl_get_label(x, fl_simulate_events(x))
cv_result <- fl_purge_cv(fl_label_index(label))
str(cv_result, max.level = 2)
```

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible 
example on [GitHub](https://github.com/yimi97/finma/issues).

More details on these concepts can be found in the great reference given below.

## Reference

1. Prado, M. L. (2018). Advances in financial machine learning. New Jersey: 
   Wiley. 
